Robust Energy-Aware Routing with Uncertain Traffic Demands

### 2014-11-20 paper.tex
remove connectivity threhold

So before going ahead our algorithm, there is another thing we should done, what is the threhold for the graph.
It does matter for what we concern most of the graph, in our graph, we choose two threholds, one is connectivity and
another is power consumption. For considering connectivity , we defined the difference of connectivity between 
two graphs as:
\begin{equation}
	diff_c = \lambda_2(G_{S, l}^o) / \lambda_2(G^o) * 100
\end{equation}
where $\lambda_2(G_{S, l}^o)$ is the extend algebraic connectivity of the final graph, when the links set $S$ and 
link $l$ are both removed from the origin graph $G^o$, and the $\lambda_2(G^o)$ is the extend algebraic connectivity of 
the origin graph.

If we set $diff_c$ valued 90\%, it means that whenever we try to remove the link $l$ from the origin graph in 
iteration, the extend algebraic connectivity should never lower than the 90\% of origin one. For power consumption
consideration, we simply take an power model from `Green TE` showed in Table xx, and defined the difference of 
power consumption between two graphs as:
\begin{equation}
	diff_p = \rho(G_{S, l}^o) / \rho(G^o) * 100
\end{equation}
where $\rho(G^o)$ is the power consumption of the origin graph, and $\rho(G_{S, l}^o)$ is similar with the 
definition above.

>>>>

So before going ahead our algorithm, there is another thing we should done, what is the threhold for the graph.
It does matter for what we concern most of the graph, in our graph, we choose the power consumption. 
We simple take an power model from `Green TE` showed in Table xx, and defined the difference of power consumption 
between two graphs as:
\begin{equation}
	diff_p = \rho(G_{S, l}^o) / \rho(G^o) * 100
\end{equation}
where $\rho(G_{S, l}^o)$ is the power consumption of the final graph, when the links set $S$ and 
link $l$ are both removed from the origin graph $G^o$, and the $\rho(G^o)$ is the power consumption of 
the origin graph.

If we set $diff_c$ valued 90\%, it means that whenever we try to remove the link $l$ from the origin graph in 
iteration, the power consumption should never lower than the 90\% of origin one. In another words, the output 
of this phase protect as much connectivity as possible
